Classifying galaxy spectra at $0.5<z<1$: an unsupervised approach

### 2017-06-17 answer_to_second_referee_comments.tex

This paper proposes the use of self-organizing maps (1D and 2D) to aid in classifying galaxy spectra.  The revision has addressed several points and improve the clarity of the text.  However, there are several remaining issues.

1. The authors did not address my comment about the significance of the work.  What was learned?  What method is advocated, and what is the evidence for its superiority?

The sentence that was added about 1D vs. 2D maps comes very late in the paper and is quite abstract, stating that the two methods are complementary.  The Introduction should establish the goals of the investigation so the reader understands the purpose of each experiment as well as its significance.

--- We have reorganized the last two paragraphs of Section 1 and added text to better describe the goal of the investigation: comparing different methods of classifying galaxy spectra against templates, with a focus on self-organizing maps. We have added additional text in Sections 4.2 and 5 comparing 1D and 2D SOMs.
%TBD: 
We have also added some text to Section 5 discussing the significance.

The paper claims that "Compared to previous attempts to classify this sample, the self-organizing map approach was able to better classify the spectra which had similarities with more than one template." (abstract), but I cannot find a quantitative comparison with any previous results.  Figure 9 is presented as the result to compare with previous work, but since the previous results are not presented nor summarized, the reader can't tell how they differ.  The paper reports "more precision", but this is not defined; does it mean smaller error bars?  Stronger correlation?  How does this show "better classification"?  To support such a claim, this paper needs to select a performance metric and report on the values achieved in these experiments, compared to other methods.
--- We selected several performance metrics. Two of them (an agreement score and the Fleiss kappa score) measure the degree to which the classifications agree. As a measure of the classification performance, we calculate the dispersion in properties of the galaxies in each class and compare these values between methods. The results of this analysis are discussed in Section 4.4.

I had suggested comparing the results to a simple nearest-neighbor classification baseline, but this was not addressed.
--- We apologize for missing this helpful suggestion in the previous version. This is now part of the analysis described in the paragraph above; the results appear in Section 4.4.

The comment about how SOMs provide an ordered clustering of the data (with respect to feature values), which k-means does not, is certainly true.  But the paper must then explain why this is important or valuable.
--- We have added text to the end of both Section 4.2 (formerly section 4.1) and Section 5 explaining the utility of an ordered clustering.

@@

On page 2, lines 29-31, the authors added this text: "An SOM can be trained without supervision and its results used to classify other data. Therefore, this method can be considered as (semi)-supervised." As written, the phrase "this method" seems to refer to SOMs (so the statement wouldn't be true - SOMs are fully unsupervised), but I think instead the authors' proposed method (of building an SOM and then applying it to classify new data, using labels on the SOM-grouped data) is what is meant.  Please clarify.
--- Changed to: 
    "The training of a self-organizing map is fully unsupervised.
     Using the resulting map as a template to classify other data requires labelling the output, which is why some groups consider self-organizing maps to be a (semi)-supervised method."

3. The inclusion of k-means helps give useful context to this work. Figure 10 shows a head-to-head comparison of k-means and SOM applied to the 12 templates using 4 clusters/nodes.  But I can't tell which one is better.  The text states that they are similar but "show discrepancies for spectra types between the extreme cases".  Which ones?  How can I tell from this figure?
--- The text describing the differences between the K-means and SOM classification of the templates (in particular, which templates are grouped together by the two methods) has been rewritten and moved to Section 4.1 (newly added in this revision).

### 2017-06-17 main.tex
Moving around text, working on ref letter

\documentclass[useAMS,usenatbib]{mn2e}
\usepackage{amsmath}
\usepackage{hyperref}
\hypersetup{
    colorlinks=True,
    linkcolor=red,
    filecolor=magenta,      
    urlcolor=cyan,
    citecolor=blue,
}
\usepackage{graphicx}
\usepackage{natbib}
\bibliographystyle{mn2e}
\usepackage{times}
\usepackage{float}
%\usepackage{caption}
\usepackage{subcaption}
\usepackage{multirow}
\usepackage{color,soul}
\usepackage{import}
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}
\usepackage{amssymb}	% Extra maths symbols
\usepackage{multicol}        % Multi-column entries in tables
\usepackage{bm}		% Bold maths symbols, including upright Greek
\usepackage{pdflscape}	% Landscape pages
%\usepackage{booktabs,fixltx2e}
\usepackage[flushleft]{threeparttable}
\usepackage{pgffor}

@@

\title[Classifying high-$z$ galaxy spectra]{Classifying galaxy spectra at $0.5<z<1$: an unsupervised approach}
%\author{rahmani.sahar}
\date{\today}
\author[S.~Rahmani, H.~Teimoorinia and P.~Barmby]{S.~Rahmani$^{1,2}$\thanks{E-mail:
srahma49@uwo.ca}, H.~Teimoorinia$^{3}$, P.~Barmby$^{1,2}$\\
$^{1}$Department of Physics $\&$ Astronomy, Western University, London, ON N6A 3K7, Canada\\
$^{2}$Centre for Planetary Science \& Exploration, Western University, London, ON N6A 3K7, Canada\\
$^{3}$Department of Physics $\&$ Astronomy, University of Victoria, Finnerty Road, Victoria, British Columbia, V8P 1A1, Canada}
\maketitle

>>>>

\documentclass[useAMS,usenatbib]{mn2e}
\usepackage{amsmath}
\usepackage{hyperref}
\hypersetup{
    colorlinks=True,
    linkcolor=red,
    filecolor=magenta,      
    urlcolor=cyan,
    citecolor=blue,
}
\usepackage{graphicx}
\usepackage{natbib}
\bibliographystyle{mn2e}
\usepackage{times}
\usepackage{float}
%\usepackage{caption}
\usepackage{subcaption}
\usepackage{multirow}
\usepackage{color,soul}
\usepackage{import}
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}
\usepackage{amssymb}	% Extra maths symbols
\usepackage{multicol}        % Multi-column entries in tables
\usepackage{bm}		% Bold maths symbols, including upright Greek
\usepackage{pdflscape}	% Landscape pages
%\usepackage{booktabs,fixltx2e}
\usepackage[flushleft]{threeparttable}
\usepackage{pgffor}
\usepackage{commath}	% Extra maths symbols

@@

\title[Classifying high-$z$ galaxy spectra]{Classifying galaxy spectra at $0.5<z<1$: an unsupervised approach}
%\author{rahmani.sahar}
\date{\today}
\author[S.~Rahmani, H.~Teimoorinia and P.~Barmby]{S.~Rahmani$^{1,2}$\thanks{E-mail:
srahma49@uwo.ca}, H.~Teimoorinia$^{3,4}$, P.~Barmby$^{1,2}$\\
$^{1}$Department of Physics $\&$ Astronomy, Western University, London, ON N6A 3K7, Canada\\
$^{2}$Centre for Planetary Science \& Exploration, Western University, London, ON N6A 3K7, Canada\\
$^{3}$Department of Physics $\&$ Astronomy, University of Victoria, Finnerty Road, Victoria, British Columbia, V8P 1A1, Canada\\
$^{4}$NRC Herzberg Astronomy and Astrophysics, 5071 West Saanich Road, Victoria, BC, V9E 2E7, Canada }
\maketitle
